Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-28 article.qmd
Add variable names in caption for poincare
Change dot to explicit derivatives and expand caption for SimBio example

Second-order system of an harmonic oscillator.
:::

@@

First-order system of two exponential decays.
:::

@@

$$
\begin{align}
&\begin{cases}
    \dot{A} = -2 \\
    \dot{B} = +1
\end{cases}
\\\\
&\begin{cases}
    A(0) &= 1 \\
    B(0) &= 0
\end{cases}
\end{align}
$$

Reaction system.
:::

@@

$$
\begin{align}
&\begin{cases}
    \dot{A} = -2 A^2 \\
    \dot{B} = +1 A^2
\end{cases}
\\\\
&\begin{cases}
    A(0) &= 1 \\
    B(0) &= 0
\end{cases}
\end{align}
$$

Mass-Action system.
:::

::::

>>>>

Second-order system of an harmonic oscillator,
where $\dot{x}$ is named $v$.
:::

@@

First-order system of two exponential decays,
where $y$ is named $\text{independent.x}$.
:::

@@

$$
\begin{align}
&\begin{cases}
    \frac{dA}{dt} = -2 \\
    \frac{dB}{dt} = +1
\end{cases}
\\\\
&\begin{cases}
    A(0) &= 1 \\
    B(0) &= 0
\end{cases}
\end{align}
$$

Reaction system $2A \rightarrow B$ with rate $1$.
:::

@@

$$
\begin{align}
&\begin{cases}
    \frac{dA}{dt} = -2 A^2 \\
    \frac{dB}{dt} = +1 A^2
\end{cases}
\\\\
&\begin{cases}
    A(0) &= 1 \\
    B(0) &= 0
\end{cases}
\end{align}
$$

Mass-Action system $2A \rightarrow B$ with rate $1 A^2$.
:::

Examples of similar reaction systems transforming $2A \rightarrow B$.
For mass-action systems, the rate is proportional to the reactants.
::::
